Optimal Particle Paths Around Points in $\R^2$ with Constrained Acceleration

### 2013-09-29 introduction.tex
Fixing trig in quadrilateral problem.

@@

In this paper, we first present a polar coordinate representation of a particle's position around a point and derive a set of differential equations governing the motion of the particle in this coordinate system. This allows us to devise some simple lemmas about the motion of the particle.

@@

Finally, we are able to tackle the problem of finding an optimal path around cones.

>>>>

In this paper, we shall examine optimal paths for a particle.

@@

We first present a polar coordinate representation of a particle's position around a point and derive a set of differential equations governing the motion of the particle in this coordinate system. This allows us to devise some simple lemmas about the motion of the particle.

@@

Finally, we tackle the problem of finding an optimal path around cones.

\subsection{Motivation}

The problem of finding an optimal trajectory is interesting because of its applications in physics. There are many instances where finding optimal paths is important. For instance, a race car driver wants to know the fastest way to get from one point to another so that he can win his race. For another example, imagine you are sending a spacecraft to a particular destination in space and would like the fastest means of getting there.

The space example directly motivates our model problem. On a spacecraft, there is a limited amount of acceleration that is possible (provided by thrusters). One would potentially like to navigate to a planet while moving around obstacles.

Understanding how to find optimal trajectories will provide greater insight into solving problems like these.

### 2013-09-29 path_theorems.tex

@@

\begin{corollary}
Given a 2-dimensional particle, $p$, with bounded centripetal acceleration, $a_c \le a_{c,max}$ and zero tangential acceleration, every valid optimal trajectory is constructed from line segments and circular sections of radius $R_{min}$, that are tangent at their intersections.
\end{corollary}

>>>>

\begin{theorem}
A 2-dimensional particle, $p$, traveling along a valid path, $\hat{\gamma(t)}$, from $X_1$ to $X_2$ has $\frac{d\abs{\theta(t)}}{dt} < 0$ for all $t \in [0, T_{f, \gamma}]$, unless $\norm{X_1 - X_2} < 2 R_{min}$.
\end{theorem}

\begin{proof}
Since $\theta(T_{f,\gamma}) = 0$, then if $\frac{d\abs{\theta(t)}}{dt} > 0$ at some point along the path, then $\theta{T_{f,\gamma}} < \theta{t_0} < \theta{t_c}$, so [TODO]
\end{proof}

\begin{theorem}
Given a 2-dimensional particle, $p$, it is always optimal to minimize $\frac{d\abs{\theta(t)}}{dt}$ at all $t \in [0, T_{\gamma}]$.
\end{theorem}

@@

\begin{corollary}\label{corr:optimal-path-fix-s}
Given a 2-dimensional particle, $p$, with bounded centripetal acceleration, $a_c \le a_{c,max}$ and zero tangential acceleration, every valid optimal trajectory is constructed from line segments and circular sections of radius $R_{min}$, that are tangent at their intersections.
\end{corollary}
